\input{tpl_inc.tex}

\begin{document}

\ptitle{I}{Rectangular Pool}

You are the owner of a land that can be represented as a grid $G$ of size $N \times M$, with rows numbered from $1$ to $N$, and columns numbered from $1$ to $M$.
Define $G_{i, j}$ as the cell of the grid on the row $i$ and column $j$.
Each cell of $G$ has either of the following terrains: puddle represented as \texttt{.} and dirt represented as \texttt{\#}.
A connected component of puddles are defined as a \textbf{pool}.
A connected component is a set of cells such that any two cells in the set are connected by traversing between cells that share a side.

Your land is very bizarre that, for the next $Q$ days, exactly one cell will change its type.
Formally, suppose cell at row $R$ and column $C$ change its type.
If the cell $G_{R, C}$ is a puddle, it will transform into dirt; if the cell is dirt, it will transform into a puddle.

You have an abnormal obsession to rectangles, so you will get sick if a pool is not rectangular.
A rectangular pool is defined as follows: let $r_{min}$, $r_{max}$, $c_{min}$, and $c_{max}$ as the minimum row number, maximum row number, minimum column number, and maximum column number of all puddles in the pool respectively, then there are exactly $(r_{max} - r_{min} + 1) \times (c_{max} - c_{min} + 1)$ puddles in the pool.

At the end of each day, determine if there exists any non-rectangular pool in your land!

\psection{Input}

The first line contains two integers $N$ and $M$ ($1 \le N \le M \le 1000$).
Each of the next $N$ lines contains $M$ characters of either $\texttt{.}$ or $\texttt{\#}$, where the character at $i$-th row and $j$-th column represents the type of cell $G_{i, j}$.

The next line contains an integer $Q$ ($1 \le Q \le 300\,000$).
Each of the next $Q$ lines contains two integers $R$ and $C$ ($1 \le R \le N$; $1 \le C \le M$) meaning that the cell $G_{R, C}$ change its type.

\psection{Output}

Output $Q$ lines representing the existence of non-rectangle pool at the end of each day. Each of the lines contains either $\texttt{RECTANGLES}$ if all pools are rectangular, or $\texttt{NO}$ if there exists a non-rectangular pool.

\exmp{1}{
5 5\\
\#...\#\\
\#...\#\\
\#\#\#\#\#\\
\#...\#\\
\#\#\#\#\#\\
3\\
4 3\\
1 3\\
2 3
}{
RECTANGLES\\
NO\\
RECTANGLES
}

\pagebreak

\textit{Explanation of Sample 1:} The following are the states of the land after each day:

\begin{verbatim}
#...#   #.#.#   #.#.#
#...#   #...#   #.#.#
#####   #####   #####
#.#.#   #.#.#   #.#.#  
#####   #####   #####
\end{verbatim}

After the first day, all three pools are rectangular pools.
After the second day, the pool formed by cells $(1, 2)$, $(1, 4)$, $(2, 2)$, $(2, 3)$, $(2, 4)$ is not rectangular.
All pools are rectangular again after the third day.

\exmp{2}{
3 4\\
\#\#\#\#\\
\#.\#\#\\
\#\#\#\#\\
1\\
2 2
}{
RECTANGLES
}

% \blankpage % use this if problem is only 1 page

\end{document}
