\input{tpl_inc.tex}

\begin{document}

\ptitle{F}{Food Rating}

In the new food delivery app \textit{Touch}, customers are able to rate the driver with integer scores from $L$ to $R$ inclusive.
Drivers will get a bonus based on how high their average rating is.
However, some drivers may abuse this system.
A driver delivering food to $1$ customer may get $5.0$ average rating, while another driver delivering food to $5$ customers may get $4.8$ average rating.

As the owner of the app, you need to ensure fairness in the bonus system.
To do that, you need to know: for a driver to have an average rating of exactly $X$, what is the minimum number of delivery $k$, such that there exists a scenario where the average rating given by $k$ customers is exactly $X$.
In addition to that, output any list of $k$ integers within $L$ to $R$ such that the average of the list is exactly $X$.

\psection{Input}

The first line contains a real number $X$ ($0 \le X \le 1000$).
The number $X$ contains at most $6$ digits, including both digits before and after the decimal separator (if any).

The second line contains two integers $L$ and $R$ ($1 \le L \le R \le 1000$).

\psection{Output}

If there exists a scenario where a driver can get an average rating exactly $X$, output in the first line, the minimum integer $k$ representing the minimum number of customers giving the rating. In the next line, output $k$ integers between $L$ and $R$ representing the rating given by the customers.

If there is no such scenario, output $-1$ in a single line. 

\exmp{1}{
8.6\\
1 10
}{
5\\
10 9 10 7 7
}

\textit{Explanation of Sample 1:} The average of $[10, 9, 10, 7, 7]$ is exactly $8.6$.
It can be proven such that there is no valid list with four or less integers.

\exmp{2}{
9\\
1 10
}{
1\\
9
}

\exmp{3}{
2.79\\
3 5
}{
-1
}

\blankpage % use this if problem is only 1 page

\end{document}