\input{tpl_inc.tex}

\begin{document}

\ptitle{H}{Light Control System}

There are $N$ shops, numbered from $1$ to $N$, that sell lamp switches.
There are also $M$ lamps, numbered from $1$ to $M$, that are initially switched off.

When you buy and use a switch from shop $i$, it will \textbf{toggle all} lamps in the set $S_i$.
When you toggle a lamp, it will become on if it is currently off, and it will become off if it is currently on.

You have to answer $Q$ queries, each giving you a range $L$ and $R$.
You have to find the minimum $r - l + 1$, such that $L \leq l \leq r \leq R$ and there exists a subset $T \subseteq \{ l, l+1, \ldots, r \}$ and by buying switches from all shops $t \in T$, you can switch on all the lamps.

You have to answer each query or report that it is impossible.

\psection{Input}

The first line contains three integers $N$, $M$, and $Q$ ($1 \leq N \leq 50\;000$; $1 \leq Q \leq 100\;000$; $1 \leq M \leq 30$).
Each of the next $N$ lines contains an integer $k_i$ ($1 \leq k_i \leq M$), followed by $k_i$ integers between $1$ and $M$ representing $S_i$, containing the lamp numbers that can be toggled by buying a switch from shop $i$.

The next $Q$ lines contain the queries, each giving you two integers $L$ and $R$ ($1 \leq L \leq R \leq N$) in a line.

\psection{Output}

For each query, output an integer representing the minimum value, or $-1$ if it is impossible.

\exmp{1}{
5 3 3\\
1 3\\
2 1 2\\
2 1 3\\
1 1\\
1 2\\
1 5\\
3 4\\
2 5
}{
2\\
-1\\
3
}

\textit{Explanation of Sample 1:} For the first query, you can pick $l = 1$ and $r = 2$, then you buy the switches from shop $1$ and $2$.

For the second query, there is no way to pick any $l$ and $r$ from the range $3 \leq l \leq r \leq 4$ such that you can buy switches that toggle all $M$ lamps. Therefore you have to output $-1$.

For the third query, you can pick $l = 2$ and $r = 4$, then you buy the switches from shop $2$, $3$, and $4$. It is also possible to pick $l = 3$ and $r = 5$, then you buy the switches from shop $3$ and $5$. Both ways give you $r - l + 1 = 3$.

\blankpage % use this if problem is only 1 page

\end{document}
